---
title: "PracticeSSMLR"
author: "Ahmad Firdaus Mohamed"
date: "2024-02-10"
output:
  word_document: default
  html_document: default
---

# Modelling Linear Regression

Using the same dataset (data_my.csv), analyze the relationship between variable ‘hdl’ and these covariates, ‘ldl’,’mogtt2h’,’gender’. Name the model as Model A.\
a) Write the regression model and regression estimate. (10 marks)

b) Interpret the variances between regression model and regression estimates (10 marks)

c) Add on interaction between ‘mogtt2h’ and ‘gender’ to the model and name the model  as Model B.

 Compare model A and model B using appropriate test and interpret the findings. (10 marks)

d) Predict the mean hdl level in a population with ldl = 3.5, mogtt2h = 7.0, gender = male according the Model A and Model B. (10 marks)

# Prepare Environment

```{r, echo=FALSE}
library(haven)
library(readxl)
library(gtsummary)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(broom)

```

## Read data

```{r, echo=FALSE}
Data1 <- read.csv('metabolic_syndrome.csv')
```

```{r, echo=FALSE}
Data1 <- Data1 %>%
  mutate(across(where(is.character),as_factor)) 
```

Using the same dataset (data_my.csv), analyze the relationship between variable ‘hdl’ and these covariates, ‘ldl’,’mogtt2h’,’gender’. Name the model as Model A.\
a) Write the regression model and regression estimate. (10 marks)

```{r}
Model.A <- lm(hdl~ldl + mogtt2h + gender, data = Data1)
summary(Model.A)
```

```{r}
tidy(Model.A, conf.int = T)
```

Regression Model Y= B0 + B1X1 + B2X2 + B3X + E

Regression Estimate

hdl = 1.1171 + 0.0966(ldl) - 0.0058(mogtt2h)- 0.18544(gendermale)

b) Interpret the variances between regression model and regression estimates (10 marks)

1) with every increase of 1mmol ldl, hdl changes by 0.0966 (95% CI = 0.0865. 0.1066) , when mogtt2h and gender are adjusted

2) with every increase of 1 mmol moggt2h, hdl changes by - 0.0058 (95% CI = -0.0088, -0.0028) when ldl and gender are adjusted

3) being male, the hdl changes by -0.1854 (95% CI = -0.2083, -0.1625) compared to female when ldl and mogtt2h are adjusted

c) Add on interaction between ‘mogtt2h’ and ‘gender’ to the model and name the model  as Model B.

 Compare model A and model B using appropriate test and interpret the findings. (10 marks)

```{r}
Model.B <- lm(hdl~ldl + mogtt2h + gender + mogtt2h:gender, data = Data1)
summary(Model.B)
```

```{r}
anova (Model.A, Model.B)
```

There is no significant difference between Model.A and Model.B when the significant value is set at 0.05

d) Predict the mean hdl level in a population with ldl = 3.5, mogtt2h = 7.0, gender = male according the Model A and Model B. (10 marks)

Expand Grind Method

```{r}
new_data <- expand.grid (ldl=3.5, mogtt2h=7.0, gender = "male")
```

For model A

```{r}
Predict.Model.A <- predict(Model.A, newdata = new_data)
summary(Predict.Model.A)
```

using equation

hdl = 1.1171 + 0.0966(ldl) - 0.0058(mogtt2h)- 0.18544(gendermale)

```{r}
1.1171 + (0.0966*3.5) - (0.0058*7) - 0.18544
```

For Model B

Expand Grid Method

```{r}
Predict.Model.B <- predict(Model.B, newdata = new_data)
Predict.Model.B
```

using equation

```{r}
summary(Model.B)
```

ldl = 1.128 + 0.0968 (ldl) - 0.0073(mogtt2h) - 0.2163 (gendermale) + 0.0043 (mogtt2h:gendermale)

```{r}
1.128 + (0.0968*3.5) - (0.0073*7) - 0.2163 + (0.0043*7)
```

```{r}
TableModelA <- tbl_regression(Model.A)
TableModelA
```

```{r}
TableModelB <- tbl_regression(Model.B)
TableModelB
```
