---
title: "PracticeSSMLR"
author: "Ahmad Firdaus Mohamed"
date: "2024-02-10"
output: html_document
---

# Modelling Linear Regression

Using the same dataset (data_my.csv), analyze the relationship between variable ‘hdl’ and these covariates, ‘ldl’,’mogtt2h’,’gender’. Name the model as Model A.\
a) Write the regression model and regression estimate. (10 marks)

b) Interpret the variances between regression model and regression estimates (10 marks)

c) Add on interaction between ‘mogtt2h’ and ‘gender’ to the model and name the model  as Model B.

 Compare model A and model B using appropriate test and interpret the findings. (10 marks)

d) Predict the mean hdl level in a population with ldl = 3.5, mogtt2h = 7.0, gender = male according the Model A and Model B. (10 marks)

# Prepare Environment

```{r}
library(haven)
library(readxl)
library(gtsummary)
library(ggplot2)
library(tidyverse)
library(dplyr)

```

## Read data

```{r}
Data1 <- read.csv('metabolic_syndrome.csv')
```

```{r}
DataXCL <-read_excel('peptic_ulcer.xlsx')
```

```{r}
glimpse(Data1)
```

```{r}
summary(Data1)
```

```{r}
Data1 <- Data1 %>%
  mutate(across(where(is.character),as_factor)) 
```

```{r}
summary(Data1)
```
