---
title: "Question 4 Syahid"
author: "Ahmad Firdaus Mohamed"
date: "2024-02-10"
output: word_document
---

```{r}
library(haven)
library(readxl)
library(tidyverse)
library(dplyr)
library(broom)
library(gtsummary)
library(ggplot2)
library(lattice)
library(caret)
library(pROC)
library(ResourceSelection)
library(performance)
#library(LogisticDx)
library(largesamplehl)

```

```{r}
Data1 <- read_excel('peptic_ulcer.xlsx')
Data1 <- Data1 %>%
  mutate(across(where(is.character),as_factor))
```

```{r}
summary(Data1)
```

A dataset named Q4.csv has six (6) variables. (? Dataset <https://github.com/drkamarul/data-for-RMed/blob/main/data/peptic_ulcer.xlsx>) (SYAHID)

i.  Outcome: alive or dead (the outcome variable)

ii.Sepsis: yes or no

iii. Creatinine: in mmol/L

iv. Age: in years old

v.  Perforation: size of perforation in cm

vi. Hemoglobin: in mg/dL

The **binary logistic regression analysis** was chosen to assess the relationship between the outcome and the rest of the variables.

## (a) Justify the choice of the analysis. (4 marks)

The dependant variable is dichotomous and the independent variables are numerical and categorical variables

State the assumptions for the analysis. (2 marks)

there is linearity of logit with the covariate

the outcome variable is binomial and has bernouli distribution

absence of multicollinearity

fixed errors (measured without error)

independe

independent variable

## (b) Generate a saturated model and name it as Model_Outcome. Present Model_Outcome in a table. (5 marks)

```{r}
Model_Outcome <- glm (outcome ~ sepsis + creatinine + age + perforation + hemoglobin, family = binomial(link='logit'), data = Data1) 

```

```{r}
summary(Model_Outcome)
```

```{r}
TableMLogR <- tbl_regression(Model_Outcome)
TableMLogR
```

## (c)Using Model_Outcome, compose an interaction between creatinine and sepsis. Name it as Model_Outcome_ia. Present Model_Outcome_ia in a table. (5 marks)

```{r}
Model_Outcome_ia <- glm(formula = outcome ~ sepsis + creatinine + age + perforation + hemoglobin + creatinine:sepsis , family = binomial(link = "logit"), data = Data1)
```

```{r}
summary(Model_Outcome_ia)
```

```{r}
TableMLogR.ia <- tbl_regression(Model_Outcome_ia)
TableMLogR.ia
```

## (d) For Model_Outcome_ia, write:

The logistic model. (2 marks)

E(Y) = P = (Exp\^(B0 + B1X1 + B2X2 + B3X3 + B4X4 + B5X5 + B6X6) / (1 + Exp \^ (B0 + B1X1 + B2X2 + B3X3 + B4X4 + B5X5 + B6X6))

The logit equation. (2 marks)

Logit (Y) = -12.1234 + 8.6209 (sepsisyes) + 0.0253(creatinine) + 0.0054 (age) + 0.8777 (perforation) + 0.25045 (hemoglobin) - 0.0228 (sepsisyes\*creatinine)

## (e) Using Model_Outcome_ia, generate the predicted values for Observation 1. Show your manual calculation. (4 marks)

```{r}
augment(Model_Outcome_ia)
```

```{r}
-12.1234 + (8.6209*0) + (0.0253*135) + (0.0054*42) + (0.8777*0.5) + (0.25045*18) - (0.0228*0*135)
```

## Model Assessment

### Classification Table

```{r}
fit.m <- augment(Model_Outcome_ia, type.predict = 'response') %>%
  mutate(pred.class=factor(ifelse(.fitted>0.5,'dead','alive')))
```

```{r}
confusionMatrix(fit.m$outcome,fit.m$pred.class)
```

The accuracy is 87.6%

Sensitivity is 93.5

Specificity is 76.7

```{r}
plot(Model_Outcome_ia)
```

### AUROC

```{r}
roc <- roc(Data1$outcome,Model_Outcome_ia$fitted.values)
```

```{r}
auc(roc)
```

```{r}
plot(roc)
```

### Hosmer-Lemeshow

```{r}
#fit.hl <- gof(Model_Outcome_ia, g=8)
```

### 

```{r}
#fit.hl$gof
```

p-value for HL and Oseo Rojek are all \> 0.05, hence the model is fit

```{r}
hltest(Model_Outcome_ia, G=10)
```
