---
title: "Question 3 Saufi"
author: "Ahmad Firdaus Mohamed"
date: "2024-02-11"
output: word_document
---

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(haven)
library(readxl)
library(tidyverse)
library(dplyr)
library(broom)
library(gtsummary)
library(lubridate)
library(ggplot2)
library(survival)
library(survminer)
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
Data1 <- read_dta("stroke_outcome.dta")
```

```{r}
summary(Data1)
```

```{r, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
Data1 <- Data1 %>%
  mutate(across(where(is.labelled),as_factor)) %>%
  mutate(dur=Data1$doa%--%Data1$dod)%>%
  mutate(dur=as.duration(dur)) %>%
  mutate(dur_days=dur/ddays(1))
```

3\. The dataset “stroke_outcome.dta” comes from a short prospective survival study. The variable outcome is labelled as dead (1) or alive (0) and the variable days is the duration from the start of follow-up untul the last follow-up. (SAUFI) (? Dataset [https://github.com/drkamarul/multivar_data_analysis/blob/main/data/stroke.dta)](https://github.com/drkamarul/multivar_data_analysis/blob/main/data/stroke.dta))

## a. Present and interpret the result for

\- Overall Kaplan-Meier analysis

```{r}
KM <-survfit(Surv(time = dur_days, event = event=='dead')~1, type="kaplan-meier", data = Data1)
summary(KM)
```

manually calculate for 10th observation

```{r}
(1-(2/44))*0.689
```

```{r}
ggsurvplot(KM, surv.median.line = "hv", pval = TRUE, conf.int = TRUE,risk.table = TRUE)
```

```{r}
quantile(KM, probs = c(0.25,0.5,0.75))
```

The median time for survival overall is 22 days (95% CI : 50, -)

```{r}
summary(KM,times=c(0,22))
```

At time 0, 4 events occured with the survival probability is 0.985 (95% CI : 0.970, 1.0)

At time 22, which is the median survival time, 58 event occurred. The survival probability is 0.495 (95% 0.386, 0.635).

\- Kaplan-Meier analysis on variable dm2

```{r}
KM.dm2 <-survfit(Surv(time = dur_days, event = event=='dead')~dm2, type="kaplan-meier", data = Data1)
summary(KM.dm2)
```

```{r}
ggsurvplot(KM.dm2, pval = TRUE, conf.int = TRUE,
          risk.table = TRUE, # Add risk table
          risk.table.col = "strata", # Change risk table color by groups
          linetype = "strata", # Change line type by groups
          surv.median.line = "hv", # Specify median survival
          ggtheme = theme_bw(), # Change ggplot2 theme
          palette = c("#E7B800", "#2E9FDF"))
```

```{r}
quantile(KM.dm2, probs = c(0.25,0.5,0.75))
```

```{r}
summary(KM.dm2,times=c(0,12,29))
```

Comment on the time, number of event and probability of the event for both analyses. (10 marks)

For no DM group, at time zero, 1 event occured with the survival probabilities of 99.4% (95% cI 98.1%, 100%). At time 29, which is the median survival time, 23 events had occurred, with the survival probabilities of 48.7% (95% CI 28.2, 84.2%)

For Dm group, at time zero, 3 event occured with the survival probabilities of 97.4% (95% cI 93.7%, 100%). At time 12, which is the median survival time, 34 events had occurred, with the survival probabilities of 40.2% (95% CI 8.2%, 27.0%)

The median survival is approximately 29 days for no DM group and 12 days for dm group, suggesting a good survival for no DM group compared to DM group.

## b. The analyst proposed to model the log hazard using the Cox proportional hazard (PH) model.

Comment on his proposal. (5 marks)

It is reasonable for the analyst to proceed with COX proportionate hazard because of the advantages over Kaplan-meier which include:

\
1) it's multivariable analysis

2) able to analyse both numerical and categorical independent variables

3) it's semi-parametric analysis which is better than non-parametric KM

4) KM unable to calculate log hazard, but COX PH is able to

5) COX PH also able to provide instantaneous risk.

6) COX PH able to assess confounder, and interaction in the model

## c. Estimate the Cox PH model with covariate: sex, gcs, dm2, sbp, dbp. Present the results in a table. Interpret the result for sbp and dm2. (10 marks)

```{r}
Cox1 <- coxph(Surv(time = dur_days, event= event == 'dead')~ sex + gcs + dm2 + sbp + dbp, data = Data1)
summary(Cox1)
```

```{r}
tidy(Cox1, conf.int = T)
```

```{r}
tblCox1 <- tbl_regression(Cox1)
tblCox1
```

1) With every increase of 1 mmhg sbp, the log hazard changes by 0.0001297 (95% CI -0.01109, 0.01369), when adjusted for sex, gcs, dm and dbp.

2) Being diabetic, changes the log hazard by 0.9089 (95% Ci : 0.3742, 1.4436) when adjusted for sbp, sex, gcs and dbp.

## d. Test the assumption for proportional hazard. Save the plot in the thumb-drive and write the name of the plot in the answer sheet. (5 marks)

```{r}
phm <- cox.zph(Cox1, transform = 'km', global= T)
plot(phm)
```

### Additional assumption test

```{r}
cox.zph (Cox1, transform = 'rank')

```

Except the gcs, all other individual covariate and global constant regression coefficient are more than 0.05. Hence when the significance level is set at 0.05, the proportional hazard is assumed

### Additional Prediction

```{r}
summary(Cox1)
```

Regression equation

Log Hazard = 0.1869 (sexfemale) - 0.2155(gcs) + 0.9089(dm2yes) + 0.0012(sbp) - 0.0019 (dbp)

Prediction for female, gcs 10, dmyes , sbp 120, dbp 90

```{r}
predict(Cox1,list(sex="female",gcs= 10,dm2="yes", sbp=120, dbp=90))
```

```{r}
0.1869 - (0.2155*10) + (0.9089) + (0.0012*120) - (0.0019*90)
```
