---
title: "Question 3 (Syahid)"
author: "Ahmad Firdaus Mohamed"
date: "2024-02-10"
output: word_document
---

```{r}
library(haven)
library(readxl)
library(tidyverse)
library(dplyr)
library(broom)
library(gtsummary)
library(lmtest)
library(rsq)
library(psych)
```

```{r}
Data1<- read.csv("metabolic_syndrome.csv")
```

```{r}
Data1<- na.omit(Data1)
```

```{r}
summary(Data1)

```

1\. Dataset named as Q3.csv has six (6) variables. (SYAHID) (? Dataset [https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.csv)](https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.csv))

i.  HBA1C: in percentage (the outcome variable)

ii.FBS: Fasting blood sugar in mmol/L

iii. AGE: Age of participants

iv. DMDX: History of diabetes (0 = No, 1 = Yes)

v.  MOGTT2H: 2-hours post prandial sugar in mmol/L

vi. TOTCHOL: Total cholesterol in mmol/L

## (a) The analyst has proposed two (2) candidate models:

Model_A: covariates are DMDX, FBS, and MOGTT2H

```{r}
Model_A <- lm (hba1c~ dmdx + fbs + mogtt2h, data = Data1)
```

```{r}
summary(Model_A)
```

Model_B: covariates are AGE and TOTCHOL

```{r}
Model_B <- lm (hba1c~ age + totchol, data = Data1)
```

```{r}
summary(Model_B)
```

Compare Model_A and Model_B. Show your results. (4 marks)

```{r}
anova(Model_A, Model_B)
```

When significant level is set at 0.05, there is significant difference between the 2 models.

Model A adj R-sq is 0.4498

Model B adj R-sq is 0.0407

Establish the model of your choice. Give reasons. (4 marks)

The selected model is Model A because of higher R-sq and there is significant difference between the 2 models

## (b) Using your model of choice from (a), perform a model assessment. Show the results and comment on the findings. (8 marks)

```{r}
plot(Model_A)
```

### Line

```{r}
plot(Model_A, which = 1)
```

The red line through the scatter plot straight, horizontal and not curved indicating linearity assumption is satisfied. The homoscedasticity assumption is met as the residuals are equally spread around the y = 0 line

```{r}
summary(Model_A)
```

Furthermore for each CV

```{r}
augment(Model_A)%>%
  ggplot(aes(x=fbs, y=.resid))+
  geom_point()+
  geom_smooth()
```

```{r}
augment(Model_A)%>%
  ggplot(aes(x=mogtt2h, y=.resid))+
  geom_point()+
  geom_smooth()
```

Residuals shows individual linearity against mogtt2h and fbs

### Independence

Based on study design

### Normality

```{r}
plot(Model_A, which = 2)
```

In Q-Q plot, there is curvature at head and tail indicating normality assumption is violated

```{r}
res.mod <- residuals(Model_A)
hist(res.mod)
```

However, based on histogram the residuals appear normally distributed

### Equal Variance

```{r}
plot(Model_A, which = 1)
```

horizontal line with randomly scattered data points around it observed, suggesting that the homoscedasticity assumption is satisfied.

## (c) Using Model_A, build a model with an interaction term between DMDX and FBS. Present the results in a table. (6 marks)

```{r}
Model.ia <- lm(hba1c ~ dmdx + fbs + mogtt2h + dmdx:fbs, data = Data1)
summary(Model.ia)
```

```{r}
Tblmod <- tbl_regression(Model.ia)
Tblmod
```

## (d) Write the regression equation. (4 marks)

```{r}
summary(Model.ia)
```

Y= B0 + B1X1 + B2X2 + B3X3 + B4X4

hba1c = 3.9007 - 0.688552(dmdxyes) + 0.147790 (fbs) + 0.1133(mogtt2h) + 0.1562 (dmdxyes\*fbs)
