---
title: "Question 2 (Amalina)"
author: "Ahmad Firdaus Mohamed"
date: "2024-02-10"
output: word_document
---

```{r}
library(haven)
library(readxl)
library(tidyverse)
library(broom)
library(gtsummary)
library(ggplot2)
library(lmtest)
library(car)
```

```{r}
Data1<- read.csv("metabolic_syndrome.csv")
```

```{r}
Data1 <- Data1 %>%
  mutate(across(where(is.character),as_factor)) %>%
  mutate(bmi=weight/(height^2))
```

```{r}
summary(Data1)
```

2\. Multiple linear regression ; Variables: BMI, fbs as covariates.  Hba1c as outcome  (AMALINA) (?dataset [https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.dta)](https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.dta))

## a. Write regression model and regression equation (10m)

```{r}
Model_A <- lm (hba1c ~ bmi + fbs, data = Data1)
summary(Model_A)
```

```{r}
tidy(Model_A, conf.int=T)
```

Y = B0 + B1X1 + B2X2 + Error

hba1c = 3.0571 + 0.0206(bmi) + 0.3896 (fbs) + Error

Interpretation

1)  With every increase of 1 unit bmi, the hba1c changes by 0.0206 (95% CI = 0.0144, 0.026808) when fbs is adjusted

2)  With every increase of 1 unit fbs, the hba1c changes by 0.3896 ( 95% CI = 0.3769, 0.4024) when bmi is adjusted

## b. Add interaction. Present in table (10m)

```{r}
Model_B <- lm (hba1c ~ bmi + fbs + bmi:fbs , data = Data1)
summary(Model_B)
```

```{r}
tidy(Model_B)
```

```{r}
Table.Model_B <- tbl_regression(Model_B)
Table.Model_B
```

## c. Write equation with interaction. (10m)

```{r}
tidy(Model_B, conf.int = T)
```

Y = B0 + B1X1 + B2X2 + B3X3 Error

hba1c = 3.6376 - 0.00140(bmi) + 0.2877 (fbs) + 0.0038(fbs\*bmi) + Error

1)  with increase of 1 unit bmi, the hba1c change by -0.0014 (95% CI = -0.01659, 0.01377) when fbs and fbs\*bmi are adjusted

2)  with increase of 1 unit fbs, the hba1c changes by 0.2877 (95% CI = 0.2222, 0.3531) when bmi and fbs\* bmi are adjusted

[***3) Interaction Interpretation susah, buat next time la***]{.underline}

## d. Assumptions for fitness analysis for this model. (10m)

\*\*comment on adjusted R-squared

### Linearity

```{r}
plot(Model_B, which=2)
```

Q-Q plot shows the linearity of residual assumption might be violated as the head and is curved

To compare covariate linearity with residuals

```{r}

```

```{r}
augment(Model_B) %>%
  ggplot(aes(x = fbs, y = .resid))+
  geom_point() +
  geom_smooth()
```

### Independent

This is based on study design

### Normality

```{r}
shapiro.test(Model_B$residuals)
```

p-value \<0.05, normality of residuals assumption violated

```{r}
res.mod <- residuals(Model_B)
hist(res.mod)
```

however, histogram of residuals seemed normality distributed by eye-balling

```{r}
plot(Model_B, which=2)
```

but the Q-Q plot showed there is no normality as the plot is curved at head and tail

### Equal Variance

```{r}
ncvTest(Model_B)
```

p-value \<0.05, homoscedacity assumption is violated

```{r}
bptest(Model_B)
```

p-value ,0.005, homoscedacity assumption is violated

```{r}
plot(Model_B, which = 1 )
```

```{r}
plot(Model_B)
```
