---
title: "Question 1 (Firdaus)"
author: "Ahmad Firdaus Mohamed"
date: "2024-02-10"
output: word_document
---

```{r}
library(haven)
library(here)
library(tidyverse)
library(dplyr)
library(broom)
library(gtsummary)
library(corrplot)

```

```{r}
Data1<-read_csv("metabolic_syndrome.csv")
```

```{r}
Data1<-Data1 %>%
  mutate(across(where(is.character),as_factor))
```

```{r}
summary(Data1)
```

1\. Data were collected to study factors that were related with HbA1c. The dataset is named as “metab_syndrome” and in .xlsx formats. (FIRDAUS) (? Dataset [https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.dta)](https://github.com/drkamarul/multivar_data_analysis/blob/main/data/metabolic_syndrome.dta))

A model was proposed to examine the relationship between HBA1C with these covariates: AGE, DMDX, MSBPR, FBS and HDL.

## a. Write the regression model and equation for MODEL_A. (15 marks)

```{r}
Model_A <- lm (hba1c ~ age + dmdx + msbpr + fbs + hdl, data = Data1)
```

```{r}
summary(Model_A)
```

Regression model

Y= B0 + B1X1 + B2X2 + B3X3 + B4X4 + B5X5

hba1c = 3.7738 + 0.0033(age) + 1.3374 (dmdxyes) - 0.0005 (msbpr) + 0.0043 (hdl)

## b. Add variable MDBPR to MODEL_A and name the new model as MODEL_B. Describe the effect of this addition to the model. (5 marks)

```{r}
Model_B <- lm (hba1c ~ age + dmdx + msbpr + fbs + hdl + mdbpr, data = Data1) 
summary(Model_B)
```

The effect of adding mdbr, the adjusted R-Sq changes from 0.5455 to 0.5478

## c. Perform comparison between MODEL_A and MODEL_B. Give comment. (5 marks)

```{r}
anova(Model_A, Model_B)
```

When the significant level is set at 0.005, there is significant difference between the 2 models

## d. Perform model assessment for MODEL_B. Save the relevant plots in the thumb-drive and write the names of the plots in the answer sheet. (10 marks).

Linearity for each numerical Covariate

```{r}
augment(Model_B) %>%
  ggplot(aes(x=age, y=.resid)) +
  geom_point()+
  geom_smooth()
```

```{r}
augment(Model_B) %>%
  ggplot(aes(x=msbpr, y=.resid)) +
  geom_point()+
  geom_smooth()
```

```{r}
augment(Model_B) %>%
  ggplot(aes(x=fbs, y=.resid)) +
  geom_point()+
  geom_smooth()
```

```{r}
augment(Model_B) %>%
  ggplot(aes(x=hdl, y=.resid)) +
  geom_point()+
  geom_smooth()
```

```{r}
augment(Model_B) %>%
  ggplot(aes(x=mdbpr, y=.resid)) +
  geom_point()+
  geom_smooth()
```

Independent

Based from study design

Normality of residual

```{r}
plot(Model_B)
```

## e. Predict the average value of HBA1C for a population with:

AGE = 48 years

DMDX = has history of diabetes (1)

MSBPR = 133 mmHg

MDBPR = 79 mmHg

FBS = 5.6 mmol/l

HDL = 1.3 mmol/l

Show your calculation. (5 marks)

```{r}
new_data <- expand.grid(age=48, dmdx = "yes", msbpr = 133, fbs = 5.6, hdl = 1.3, mdbpr =79)
new_data
```

```{r}
predict.Model_B <- predict(Model_B, newdata = new_data)
predict.Model_B
```

```{r}
summary(Model_B)
```

hba1c = 3.4945 + 0.0043 (age) + 1.3326(dmdxyes) - 0.0040 (msbpr) + 0.3146 (fbs) + 0.0164 (hdl) + 0.0087 (mdbpr)

```{r}
3.4945 + (0.0043*48) + 1.3326 - (0.0040*133) + (0.3146*5.6) + (0.0164*1.3) + (0.0087*79)
```
